---
title: "Homework 5"
author: "Emma Sexton <br>"
date: "Due 16 November 2022"
output: github_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include = FALSE, message = FALSE, warning = FALSE}
library(tidyverse)
library(readxl)
library(rvest)


knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

#### Import data using `list.files`

```{r, message = FALSE}
long_study_df =
  tibble(
    file_names = list.files(path = "data/problem_1/", all.files = TRUE, no.. = TRUE),
    path = str_c("data/problem_1/", file_names)
  ) %>% 
  mutate(data = map(path, read_csv)) %>% 
  unnest(cols = c(data))
```


#### Tidy data

```{r}
tidy_long_df = 
  long_study_df %>% 
  mutate(
    files = str_replace(file_names, ".csv", ""),
    group = str_sub(files, 1, 3)) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "outcome",
    names_prefix = "week_") %>% 
  mutate(week = as.numeric(week)) %>%
  select(group, subject = files, week, outcome)
```

#### Plot showing observations on each subject over time

```{r}
tidy_long_df %>% 
  ggplot(aes(x = week, y = outcome, group = subject, color = group)) + 
  geom_point() + 
  geom_path() + 
  facet_grid(~group)
```

There appears to be a positive trend in the experimental group where outcome values increase as time passes. This trend is not observed or is not as apparent in the control group. Additionally, the values in Week 8 are higher in the experimental group compared to the control, while values were similar in both groups in Week 1. 


## Problem 2

#### Importing and describing the data
```{r, message = FALSE}
homicide_df <- 
  read_csv(
    'data/problem_2/homicide-data.csv') %>%  
  janitor::clean_names()
```

Describe the raw data. Create a city_state variable (e.g. “Baltimore, MD”) and then summarize within cities to obtain the total number of homicides and the number of unsolved homicides (those for which the disposition is “Closed without arrest” or “Open/No arrest”).

Describe the Data: ***need to do***


#### Summarizing total number of homicides and number of unsolved homicides

```{r}
homicide_summary <- 
  homicide_df %>% 
  mutate(
    city_state = str_c(city, sep = ", ", state),
  ) %>% 
  group_by(city_state) %>% 
  summarise(
    n_homs = n(),
    n_unsolved = sum(disposition == "Closed without arrest" | disposition == "Open/No arrest")
  ) %>% 
  arrange(desc(n_homs))

homicide_summary %>% 
  knitr::kable(col.names = c("City, State", "Total Homicides (n)", "Unsolved Homicides(n)"), 
               caption = "Number of Homicides per City, State (in descending order)")
```


#### Estimating proportions of unsolved homicides: Running `prop.test` for Baltimore, MD

For the city of Baltimore, MD, use the `prop.test` function to estimate the proportion of homicides that are unsolved; save the output of prop.test as an R object, apply the broom::tidy to this object and pull the estimated proportion and confidence intervals from the resulting tidy dataframe.

```{r}
baltimore_hom <-
  homicide_summary %>% 
  filter(city_state == "Baltimore, MD")

baltimore_prop <-
  prop.test(
    x = baltimore_hom$n_unsolved, 
    n = baltimore_hom$n_homs
  ) %>% 
  broom::tidy() %>% 
  select(estimate, starts_with("conf"))

baltimore_prop %>% 
  knitr::kable(digits = 3, 
               col.names = c("Estimate", "Lower CI", "Upper CI"), 
               caption = "Estimated Proportion and Confidence Interval (CI) for Unsolved Homicides in Baltimore, MD")
```



#### Estimating Proportions of unsolved homicides: Running `prop.test` for each city

Now run `prop.test` for each of the cities in your dataset, and extract both the proportion of unsolved homicides and the confidence interval for each. Do this within a “tidy” pipeline, making use of `purrr::map`, `purrr::map2`, list columns and unnest as necessary to create a tidy dataframe with estimated proportions and CIs for each city.

```{r}
city_state_hom_prop <- homicide_summary %>% 
  mutate(
    results = map2(.x = homicide_summary$n_unsolved, 
                   .y = homicide_summary$n_homs, 
                   ~prop.test(x = .x, n = .y, conf.level = 0.95)),
    results = map(.x = results, 
                  ~broom::tidy(.x))
    ) %>% 
  unnest(results) %>% 
  select(city_state, estimate, starts_with("conf")) %>% 
  arrange(desc(estimate))

city_state_hom_prop %>% 
  knitr::kable(digits = 3, 
               col.names = c("City, State", "Estimate", "Lower CI", "Upper CI"), 
               label = "Estimated Proportion and Confidence Intervals (CI) for Unsolved Homicides across the United States (in descending order)")
```


#### Plot of unsolved homicide proportions and confidence intervals for each city

Create a plot that shows the estimates and CIs for each city – check out geom_errorbar for a way to add error bars based on the upper and lower limits. Organize cities according to the proportion of unsolved homicides.



## Problem 3

#### Conducting a simulation to explore power in a one-sample t-test

First, we need to set the following design elements:

```{r}
# sim_model <- function(sample_n = 30, mu, sigma = 5) {
#   
#   model_df = 
#     tibble(
#       x = rnorm(n = sample_n, mean = mu, sd = sigma),
#     )
#   
#   model_df %>% 
#     t.test(., conf.level = 0.95) %>% 
#     broom::tidy() %>% 
#     select(estimate, p.value)
#   
# }
# 
# problem_3_dataset <- 
#   5000 %>% 
#   rerun(sim_model(mu = 0))

```

A dataframe consisting of 5000 datasets, where each list contains the estimate value and the p-value for that dataset were created above. 

Next, we'll repeat this when mu = {1 ,2, 3, 4, 5, 6}:

```{r}
# mu_list = 
#   list(
#     "mu = 1" = 1
#     
#   )
# 
# output = vector("list", length = 6)
# 
# output[[1]] = sim_model(mu_list[[1]])
# 
# for(i in 1:6) {
#   
#   output[[i]] = mean_and_sd(list_norm[[i]])
# 
# }

```

