---
title: "Homework 5"
author: "Emma Sexton <br>"
date: "Due 16 November 2022"
output: github_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include = FALSE, message = FALSE, warning = FALSE}
library(tidyverse)
library(readxl)
library(rvest)


knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

```{r}
long_study_df =
  tibble(
    file_names = list.files(path = "data", all.files = TRUE, no.. = TRUE)
  ) 

  # mutate(
  #   data = purrr::map(long_study_df[["file_names"]], read.csv("data/"))
  # )

```


## Problem 2

```{r}
homicide_df <- 
  read_csv(
    'data/homicide-data.csv') %>%  
  janitor::clean_names()
```

Describe the raw data. Create a city_state variable (e.g. “Baltimore, MD”) and then summarize within cities to obtain the total number of homicides and the number of unsolved homicides (those for which the disposition is “Closed without arrest” or “Open/No arrest”).

Describe the Data: ***need to do***



```{r}
homicide_summ <- 
  homicide_df %>% 
  mutate(
    city_state = str_c(city, sep = ", ", state),
    num_homicide = ifelse(disposition == "Closed by arrest", "homicide_n", "unsolved_n")
  ) %>% 
  group_by(city_state, num_homicide) %>% 
  summarise(
    n_obs = n()
  )
```

#### Estimating Proportions of Unsolved Homicides: Running `prop.test` for Baltimore, MD

For the city of Baltimore, MD, use the `prop.test` function to estimate the proportion of homicides that are unsolved; save the output of prop.test as an R object, apply the broom::tidy to this object and pull the estimated proportion and confidence intervals from the resulting tidy dataframe.

```{r}
baltimore_hom <- homicide_summ %>% 
  filter(city_state == "Baltimore, MD") %>% 
  mutate(
    sum_homicides = sum(n_obs),
    test = broom::tidy(prop.test(n_obs, sum_homicides, conf.level = 0.95))
  )
```


#### Estimating Proportions of Unsolved Homicides: Running `prop.test` for each city

Now run `prop.test` for each of the cities in your dataset, and extract both the proportion of unsolved homicides and the confidence interval for each. Do this within a “tidy” pipeline, making use of `purrr::map`, `purrr::map2`, list columns and unnest as necessary to create a tidy dataframe with estimated proportions and CIs for each city.

```{r}
# unsolved_prop = function(df) {
#   
#   unsolved_hom <- homicide_summ %>%
#   mutate(
#     sum_homicides = sum(n_obs),
#     test = broom::tidy(prop.test(n_obs, sum_homicides, conf.level = 0.95))
#   )
#   
# }
# 
# test_df <- homicide_summ %>% 
#   map(., unsolved_prop) %>% 
#   tidyr::unnest(test_df)


```


#### Plot of Unsolved Homicide Proportions and Confidence Intervals Across the U.S.

Create a plot that shows the estimates and CIs for each city – check out geom_errorbar for a way to add error bars based on the upper and lower limits. Organize cities according to the proportion of unsolved homicides.




