---
title: "Homework 5"
author: "Emma Sexton <br>"
date: "Due 16 November 2022"
output: github_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include = FALSE, message = FALSE, warning = FALSE}
library(tidyverse)
library(readxl)
library(rvest)


knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
  fig.width = 8,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

### Import data using `list.files`

```{r, message = FALSE}
longitudinal_study_df =
  tibble(
    file_names = list.files(path = "data/problem_1/", all.files = TRUE, no.. = TRUE),
    path = str_c("data/problem_1/", file_names)
  ) %>% 
  mutate(data = map(path, read_csv)) %>% 
  unnest(cols = c(data))
```


### Tidy data

```{r}
tidy_longitudinal_df = 
  longitudinal_study_df %>% 
  mutate(
    files = str_replace(file_names, ".csv", ""),
    group = str_sub(files, 1, 3)) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "outcome",
    names_prefix = "week_") %>% 
  mutate(week = as.numeric(week)) %>%
  select(group, subject = files, week, outcome)
```

### Plot showing observations on each subject over time

```{r}
tidy_longitudinal_df %>% 
  ggplot(aes(x = week, y = outcome, group = subject, color = group)) + 
  geom_point() + 
  geom_path() + 
  facet_grid(~group)
```

There appears to be a positive trend in the experimental group where outcome values increase as time passes. This trend is not observed or is not as apparent in the control group. Additionally, the values in Week 8 are higher in the experimental group compared to the control, while values were similar in both groups in Week 1. 


## Problem 2

### Importing and describing the data
```{r, message = FALSE}
homicide_df <- 
  read_csv(
    'data/problem_2/homicide-data.csv') %>%  
  janitor::clean_names()

skimr::skim(homicide_df)
```

**Summary of Dataset**: The above dataset (`homicide_df`) consists of `r nrow(homicide_df)` observations and `r ncol(homicide_df)` variables. The dataset details case information, such as case ID (`uid`) and the date the homicide was reported (`reported_date`). Additionally, information related to the victim (`victim_last`, `victim_first`, `victim_race`, `victim_age`, `victim_sex`) is detailed, as well as the location of the homicide (`city`, `state`, `lat`, `lon`). Lastly, a categorical variable (`disposition`) consists of three levels to detail the results of the homicide (i.e., "Closed without arrest", "Closed with arrest", and "Open/No arrest"). 

There is no missing data except for `r sum(is.na(homicide_df$lat))` missing values in `lat` and `r sum(is.na(homicide_df$lat))` missing values in `lon`. 


### Summarizing total number of homicides and number of unsolved homicides

To summarize the homicide data, we will generate a new variable (`city_state`) and count the total number of homicides reported in each city, as well as the number of unsolved homicides, determined by the `disposition` variable (i.e., "Closed without arrest" or "Open/No arrest"). 

```{r}
homicide_summary <- 
  homicide_df %>% 
  mutate(
    city_state = str_c(city, sep = ", ", state),
  ) %>% 
  group_by(city_state) %>% 
  summarise(
    n_homs = n(),
    n_unsolved = sum(disposition == "Closed without arrest" | disposition == "Open/No arrest")
  ) %>% 
  arrange(desc(n_homs))

homicide_summary %>% 
  knitr::kable(col.names = c("City, State", "Total Homicides (n)", "Unsolved Homicides(n)"))
```

The above dataset (`homicide_summary`) details the total number of homicides and the number of unsolved homicides that have occurred in each city. Arranging the data based on the number of homicides demonstrates that Chicago, IL, Philadelphia, PA, and Houston, TX have the highest number of total homicides. 


### Estimating proportions of unsolved homicides: Running `prop.test` for Baltimore, MD

```{r}
baltimore_hom <-
  homicide_summary %>% 
  filter(city_state == "Baltimore, MD")

baltimore_prop <-
  prop.test(
    x = baltimore_hom$n_unsolved, 
    n = baltimore_hom$n_homs
  ) %>% 
  broom::tidy() %>% 
  select(estimate, starts_with("conf"))

baltimore_prop %>% 
  knitr::kable(digits = 3, 
               col.names = c("Estimate", "Lower CI", "Upper CI"))
```

The above dataset (`baltimore_prop`) depicts the proportion of unsolved homicides in Baltimore, MD in addition to the estimate's upper and lower limit of the 95% confidence interval. The proportion of unsolved homicides in Baltimore is `r round(baltimore_prop$estimate, 3)` (95% CI: `r round(baltimore_prop$conf.low, 3)`-`r round(baltimore_prop$conf.high, 3)`). 


### Estimating Proportions of unsolved homicides: Running `prop.test` by city

```{r}
city_state_hom_prop <- homicide_summary %>% 
  mutate(
    results = map2(.x = homicide_summary$n_unsolved, 
                   .y = homicide_summary$n_homs, 
                   ~prop.test(x = .x, n = .y, conf.level = 0.95)),
    results = map(.x = results, 
                  ~broom::tidy(.x))
    ) %>% 
  unnest(results) %>% 
  select(city_state, estimate, starts_with("conf")) %>% 
  arrange(desc(estimate))

city_state_hom_prop %>% 
  knitr::kable(digits = 3, 
               col.names = c("City, State", "Estimate", "Lower CI", "Upper CI"))
```

The above dataset (`city_state_hom_prop`) depicts the estimated proportion of unsolved homicides, as well as each estimate's 95% confidence interval for each city. By arranging the dataset in descending order, it is apparent that Chicago, IL has the highest proportion of unsolved homicides, followed by New Orleans, LA and Baltimore, MD.  


### Plot of unsolved homicide proportions and confidence intervals by city

```{r}
city_state_hom_prop %>% 
  mutate(
    city_state = fct_reorder(city_state, -estimate)
  ) %>% 
  ggplot(aes(x = city_state, y = estimate, color = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  labs(
    title = "Estimated Proportion of Unsolved Homicides Across the United States",
    x = "City, State",
    y = "Estimated Proportion"
  ) + 
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(angle = 60, hjust = 1),
        legend.title = element_blank())
```

The above plot demonstrates the estimated proportion of unsolved homicides in each city, with its corresponding confidence interval demonstrated using error bars. As noted in previous analyses, Chicago, IL has the highest proportion of unsolved homicides, while Tulsa, AL has the lowest proportion. Of note, Tulsa, AL only has one reported homicide, and therefore the Chi-Squared approximation calculated using `prop.test` may not be accurate. 



## Problem 3

### Conducting a simulation to explore power in a one-sample t-test

First, we need to set the following design elements:

```{r}
# sim_model <- function(sample_n = 30, mu, sigma = 5) {
#   
#   model_df = 
#     tibble(
#       x = rnorm(n = sample_n, mean = mu, sd = sigma),
#     )
#   
#   model_df %>% 
#     t.test(., conf.level = 0.95) %>% 
#     broom::tidy() %>% 
#     select(estimate, p.value)
#   
# }
# 
# problem_3_dataset <- 
#   5000 %>% 
#   rerun(sim_model(mu = 0))

```

A dataframe consisting of 5000 datasets, where each list contains the estimate value and the p-value for that dataset were created above. 

Next, we'll repeat this when mu = {1 ,2, 3, 4, 5, 6}:

```{r}
# mu_list = 
#   list(
#     "mu = 1" = 1
#     
#   )
# 
# output = vector("list", length = 6)
# 
# output[[1]] = sim_model(mu_list[[1]])
# 
# for(i in 1:6) {
#   
#   output[[i]] = mean_and_sd(list_norm[[i]])
# 
# }

```

